Transfer Learning in Visual and Relational Reasoning

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/related_work.tex

\tk{missing review: TL in visual reasoning, refer to CoGenT and COG}

\tk{after reading that section the reader should end up with a conclusion that: there are no good models for TL in VR and, moreover, the datasets are randomly testing this or that, there is no theoretical framework showing that do they mean/bigger picture is missing}

>>>>

In Visual Reasoning, transfer learning has helped models generalize better to domains with different distributions. Using the CLEVR-CoGenT~\cite{johnson2017clevr} dataset and finetuning, \cite{mascharka2018transparency, perez2018film, johnson2017inferring} have demonstrated impressive accuracy gains on a domain with different attributes combinations than the one used for training. Similarly, using the COG dataset, \cite{yang2018dataset} have shown that a different model can do significantly better than chance on a task it was not explicitly trained on, by using knowledge learned on other tasks.

These results clearly indicate the usefulness of transfer learning, despite the assumption of similar distributions between the source and target domains not being respected. As this is currently not fully understood, it highlights the need for a more systematic research direction on these topics.
We propose to address this by introducing a taxonomy of transfer learning in visual reasoning, and illustrate it with two visual reasoning datasets.

% \tk{The experimental results clearly indicate that transfer learning is helping, despite that the core assumptions on the compatibility/similarity of domains is broken (transfering between domains having similar distribution).
% We do not understand this fully, thus the need for a more systematic research on that topic emerges.
% The paper adresses that by introducing a theoretical framework/taxonomy enabling to categorise visual reasoning tasks.
% As a starting point, we picked two visual reasoning datasets and analyse the achieved results through the prism of the proposed taxonomy.
% }
%
%
% \tk{after reading that section the reader should end up with a conclusion that: there are no good models for TL in VR and, moreover, the datasets are randomly testing this or that, there is no theoretical framework showing that do they mean/bigger picture is missing}
